### 2020-04-05 Thesis-Glossary.tex
Write more background

% Start terms
\newterm{clipperchip}{Clipper Chip}{
    A 1993 initiative by the Clinton administration to provide ``the public with strong cryptographic tools without
    sacrificing the ability of law enforcement and intelligence agencies to access unencrypted versions of those
    communications'' via hardware additions to consumer electronics. The proposal faced opposition, and died in 1994
    when security researcher Matt Blaze discovered flaws that allowed users to subvert the Clipper Chip mechanisms
}

@@

\newterm{public-key-crypto}{public key cryptography}{
    Another name for asymmetric encryption
}
\newterm{asym-crypto}{asymmetric cryptography}{
    A cipher scheme where encryption and decryption are performed with separate, paired keys, called the public key and
    the private key
}
\newterm{sym-crypto}{symmetric cryptography}{
    A cipher scheme where encryption and decryption are performed with the same key
}
% End terms

@@

% Start acronyms
\newabbreviation{AECA}{AECA}{Arms Export Control Act}
\newabbreviation{AV}{AV}{anti-virus}
\newabbreviation{AWA}{AWA}{All Writs Act}
\newabbreviation{CALEA}{CALEA}{Communications Assistance for Law Enforcement Act}
\newabbreviation{CFAA}{CFAA}{Computer Fraud and Abuse Act}
\newabbreviation{CP}{CP}{child pornography}
\newabbreviation{CSAM}{CSAM}{child sexual abuse material}
\newabbreviation{DE}{DE}{device encryption}
\newabbreviation{DIM}{DIM}{data in motion}
\newabbreviation{DAR}{DAR}{data at rest}
\newabbreviation{E2E}{E2E}{end to end}
\newabbreviation{EA}{EA}{exceptional access}
\newabbreviation{ECPA}{ECPA}{Electronic Communications Privacy Act}
\newabbreviation{ED}{ED}{ephemeral data}
\newabbreviation{FBI}{FBI}{Federal Bureau of Investigation}
\newabbreviation{FISA}{FISA}{Foreign Intelligence Surveillance Act}
\newabbreviation{FISAAA}{FISAAA}{FISA Amendments Act}
\newabbreviation{FISC}{FISC}{Foreign Intelligence Surveillance Court}
\newabbreviation{ITAR}{ITAR}{International Traffic in Arms Regulations}
\newabbreviation{KEK}{KEK}{key encrypting key}
\newabbreviation{LE}{LE}{law enforcement}
\newabbreviation{LEA}{LEA}{law enforcement agency}
\newabbreviation{LEO}{LEO}{law enforcement officer}
\newabbreviation{NED}{NED}{non-ephemeral data}
\newabbreviation{NSA}{NSA}{National Security Agency}
\newabbreviation{NSL}{NSL}{National Security Letter}
\newabbreviation{PAA}{PAA}{Protect America Act}
\newabbreviation{PGP}{PGP}{Pretty Good Privacy}
\newabbreviation{PIN}{PIN}{personal identification number}
\newabbreviation{PKI}{PKI}{public key infrastructure}
\newabbreviation{PW}{PW}{password}
\newabbreviation{SE}{SE}{strong encryption}
\newabbreviation{SSO}{SSO}{single sign-on}
\newabbreviation{TLS}{TLS}{Transport Layer Security}
\newabbreviation{VPN}{VPN}{virtual private network}
% End acronyms

>>>>

% Start terms
\newterm{the-cw1}{the first crypto war}{
    The flurry of evolution and conflict in encryption policy during the 1990s, characterized by episodes around export
    controls, \ac{PGP}, the \ac{clipperchip}, and early key escrow proposals
}
\newterm{the-cw2}{the second crypto war}{
    The flurry of conflict in encryption policy during the late 2010s to present, characterized by angst from the
    Snowden revelations, the proliferation of strong encryption, and the Apple vs. FBI case
}

\newterm{clipperchip}{Clipper Chip}{
    A 1993 initiative by the Clinton administration to provide ``the public with strong cryptographic tools without
    sacrificing the ability of law enforcement and intelligence agencies to access unencrypted versions of those
    communications'' via hardware additions to consumer electronics. The proposal faced opposition, and died in 1994
    when security researcher Matt Blaze discovered flaws that allowed users to subvert the Clipper Chip mechanisms
}

@@

\newterm{public-key-crypto}{public key cryptography}{
    Another name for asymmetric encryption
}
\newterm{asym-crypto}{asymmetric cryptography}{
    A cipher scheme where encryption and decryption are performed with separate, paired keys, called the public key and
    the private key
}
\newterm{sym-crypto}{symmetric cryptography}{
    A cipher scheme where encryption and decryption are performed with the same key
}

\newterm{forward-secrecy}{forward secrecy}{
    A property of \ac{DIM} encryption protocols that ensures that a leaked private key or session key does not
    compromise any other private key or session key
}
\newterm{replay-protection}{replay protection}{
    A property of \ac{DIM} encryption protocols that ensures that messages cannot be replayed by an attacker without
    detection
}

\newterm{disk-encryption}{disk encryption}{
    An application of ecnryption for \ac{DAR} that involves encrypting the contents
}
% End terms

@@

% Start acronyms
\newabbreviation{AECA}{AECA}{Arms Export Control Act}
\newabbreviation{AV}{AV}{anti-virus}
\newabbreviation{AWA}{AWA}{All Writs Act}
\newabbreviation{CALEA}{CALEA}{Communications Assistance for Law Enforcement Act}
\newabbreviation{CFAA}{CFAA}{Computer Fraud and Abuse Act}
\newabbreviation{CP}{CP}{child pornography}
\newabbreviation{CSAM}{CSAM}{child sexual abuse material}
\newabbreviation{DE}{DE}{device encryption}
\newabbreviation{DIM}{DIM}{data in motion}
\newabbreviation{DAR}{DAR}{data at rest}
\newabbreviation{E2E}{E2E}{end to end}
\newabbreviation{E2EE}{E2EE}{end to end encryption}
\newabbreviation{EA}{EA}{exceptional access}
\newabbreviation{ECPA}{ECPA}{Electronic Communications Privacy Act}
\newabbreviation{ED}{ED}{ephemeral data}
\newabbreviation{FBI}{FBI}{Federal Bureau of Investigation}
\newabbreviation{FISA}{FISA}{Foreign Intelligence Surveillance Act}
\newabbreviation{FISAAA}{FISAAA}{FISA Amendments Act}
\newabbreviation{FISC}{FISC}{Foreign Intelligence Surveillance Court}
\newabbreviation{ITAR}{ITAR}{International Traffic in Arms Regulations}
\newabbreviation{KEK}{KEK}{key encrypting key}
\newabbreviation{LE}{LE}{law enforcement}
\newabbreviation{LEA}{LEA}{law enforcement agency}
\newabbreviation{LEO}{LEO}{law enforcement officer}
\newabbreviation{NED}{NED}{non-ephemeral data}
\newabbreviation{NSA}{NSA}{National Security Agency}
\newabbreviation{NSL}{NSL}{National Security Letter}
\newabbreviation{PAA}{PAA}{Protect America Act}
\newabbreviation{PGP}{PGP}{Pretty Good Privacy}
\newabbreviation{PIN}{PIN}{personal identification number}
\newabbreviation{PKI}{PKI}{public key infrastructure}
\newabbreviation{PW}{PW}{password}
\newabbreviation{SE}{SE}{strong encryption}
\newabbreviation{SSO}{SSO}{single sign-on}
\newabbreviation{TLS}{TLS}{Transport Layer Security}
\newabbreviation{VPN}{VPN}{virtual private network}
% End acronyms
